### 2015-11-30 fundamentals/impl.tex
line 670: fixes automoated->automated
line 339: fleshing out the superior -> flexible statement a bit

Furthermore, the \gls{ABM} paradigm more flexible than the system dynamic approach used in current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@

Autmoated testing including \gls{CI} is a necessary but not sufficient
component of the \Cyclus \gls{QA} system: it keeps bad code out of
\Cyclus. However, \Cyclus will always require human eyes and hands to let good
code in.

>>>>

Furthermore, the \gls{ABM} paradigm more flexible and intuitive (from both a developer and user perspective) than the system dynamic approach used in current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@

Autmated testing including \gls{CI} is a necessary but not sufficient
component of the \Cyclus \gls{QA} system: it keeps bad code out of
\Cyclus. However, \Cyclus will always require human eyes and hands to let good
code in.
